\stktokens{}: Enforcing Well-Bracketed Control Flow and Stack Encapsulation Using Linear Capabilities

### 2020-03-11 popl-2019-journal-v/discussion.tex
Full pass over paper, ready to submit?

\begin{jversion}
  A compiler is secure when it enforces the properties of high-level languages which begs the question what properties should we enforce.
  When it comes to fully-abstract compilation, then the answer is that all the properties of the high-level language should be enforced, so the real question is what high-level language we would like.
  \stktokens{} ensures a standard call-return control-flow, but if we want a different kind of control-flow, for instance call/CC, then we need to come up with a different enforcement scheme.
  Further, many high-level languages have exceptions which is yet another form of control-flow which is also not supported by \stktokens{}.
  This goes to show how we must consider what high-level language we want in order to answer the question of what properties we must enforce to get a fully-abstract compiler.
  % Lau: Say something about address hiding?

@@

  % TODO new paragraph: Machine checked proof. MANY details, any future work should be machine checked?
  One challenge in full-abstraction proofs is to relate the translation of program to the program it was translated from.
  Such a relation is often expressed as a back-translation  \citep{devriese_modular_2017}, i.e.\ a translation from the target language to the source language.
  When we use an overlay semantics, the back-translation becomes trivial because the source and target language are syntactically the same, so the identity can be used as the back-translation.
  If we have native call and return instructions in the source language, then the source language would be different from the target language, and we would have to use a non-trivial back-translation.
  Specifically, the back-translation would need to distinguish sequences of instructions that is the translation of a call from sequences of instructions that just look like a call.
  With overlay semantics, this is not a concern because everything that looks like a call is interpreted as a call.
\end{jversion}

>>>>

\begin{jversion}
  A compiler is secure when it enforces the properties of high-level languages which begs the question what properties we should enforce.
  When it comes to fully-abstract compilation, then the answer is that all the properties of the high-level language should be enforced, so the real question is what high-level language we would like.
  \stktokens{} ensures a standard call-return control-flow, but if we want a different kind of control-flow, for instance call/CC, then we need to come up with a different enforcement scheme.
  Further, many high-level languages have exceptions as another form of control-flow not (yet) supported by \stktokens{}.
  This goes to show how we must consider what high-level language we want in order to answer the question of what properties we must enforce to get a fully-abstract compiler.
  % Lau: Say something about address hiding?

@@

  % TODO new paragraph: Machine checked proof. MANY details, any future work should be machine checked?
  One challenge in full-abstraction proofs is to construct source language contexts that emulate the behavior of an arbitrary target language context.
  This construction is known as a back-translation  \citep{devriese_modular_2017}, i.e.\ a translation from the target language to the source language.
  When we use an overlay semantics, the back-translation becomes trivial because the source and target language are syntactically the same, so the identity can be used as the back-translation.
  If we have native call and return instructions in the source language, then the source language would be different from the target language, and we would have to use a non-trivial back-translation.
  Specifically, the back-translation would need to distinguish sequences of instructions that is the translation of a call from sequences of instructions that just look like a call.
  With overlay semantics, this is not a concern because everything that looks like a call is interpreted as a call.
\end{jversion}
